  I am a full stack software engineer able to design and code all layers of a modern application: browser, application server, database.
  I have worked with a variety of technologies in all tiers. In the browser: from vanilla HTML/CSS/JavaScript, jQuery to using UI component
  libraries like jQuery UI or DHTMLX, to Webpack / ReactJS. In the application server I've experience with Java stacks
  deployed in Tomcat or JBoss servers with both presentation oriented (Spring Web MVC / JSP) and
  service-oriented (JAX-RS, SOAP, Restlet, Jersey, RESTEasy) applications. In the database I have experience with Sybase, Oracle,
  MySQL and PostgreSQL databases.
  I am a proficient Emacs user (with an Emacs setup that I've honed over the years for maximum productivity)
  and I like to live as close to the command line as possible
  (though I can of course also use an IDE
  if required). In addition to writing the code I can
  handle the build system (Ant / Ivy), unit testing, static code analysis, coding standards and automatic compliance checking
  , code coverage,
  integration testing, shell-scripting, etc.
  I am also proficient  in JavaScript-the-language (ECMAScript 6) including
  the Node / Babel / Webpack ecosystem and the Mocha (unit tests) and FlowType (type checking and static code analysis) tools.


  My career spans almost 2 decades of software development and technical project management in all manners of companies
  from start-ups and SMEs to world class organizations
  such as the \href{http://www.esa.int/About_Us/ESAC}{European Space Agency} and the
  \href{https://www.cfa.harvard.edu/}{Harvard-Smithsonian Center for Astrophysics} (my current position).

  In my free time I study Math and develop JavaScript games which you can play at:
  \href{https://mperdikeas.github.com/games.html}{https://mperdikeas.github.com/games.html}.
    %\hairspace{}---\hairspace{}I am also currently exploring ReactJS in my free time.


  
